RAM-SCB may be used as a component to the Space Weather Modeling Framework. Under this mode, RAM-SCB receives initial and boundary conditions from the Framework's other components and returns plasma properties to create a two-way coupled system.

%INSERT TABLE OF COUPLING DESCRIPTIONS.

\section{Installing RAM-SCB as a SWMF Component}
% QUESTION: Should this entire section just be rewritten? SWMF no longer uses CVS, we have changed the coupling on our end a bit. And SWMF has changed the coupling on their end a lot. Honestly, it may be of more use to have an entirely seperate document for the SWMF coupling as it has its own set of installation instructions and its own set of difficulties.
 
Obtain a copy of the SWMF and, if necessary, unpack the tarball.  Descend into the Inner Magnetosphere (IM) directory of the Framework.  This is where all inner magnetosphere-type codes used by the Framework are located.  Copy the entire RAM-SCB directory here as {\tt RAM\_SCB}.  It is important to name the directory correctly. CVS users should note that checking out RAM-SCB directly into the SWMF directories will be tricky because of conflicting CVS files located in each Framework directory. Use CVS carefully! 

Next, move or remove the share directory. RAM-SCB will be using the version obtained through the SWMF. Additionally, making RAM-SCB's share directory unavailable signals RAM-SCB to go into component mode.

Installing the SWMF and RAM-SCB happens concurrently using the Config.pl script from the top-level directory of the SWMF.  

