
1. Jordanova, V. K., L. M. Kistler, J. U. Kozyra, G. V. Khazanov, and A. F. Nagy. Collisional losses of ring current ions. {\it J. Geophys. Res., 101}, 111, 1996.
\\
2. Jordanova, V. K., Y. S. Miyoshi, S. Zaharia, M. F. Thomsen, G. D. Reeves, D. S. Evans, C. G. Mouikis, and J. F. Fennell. Kinetic simulations of ring current evolution during the Geospace Environment Modeling challenge events, {\it J. Geophys. Res., 111}, A11S10, October 2006. doi:10.1029/2006JA011644.
\\
3. Jordanova, V. K., S. Zaharia, and D. T. Welling. Comparative study of ring current development using empirical, dipolar, and self-consistent magnetic field simulations. {\it Journal of Geophysical Research (Space
Physics)}, 115(A14):A00J11, December 2010. doi: 10.1029/2010JA015671. 
\\
4. Rasmussen, C. E., S. M. Guiter, and S. G. Thomas, Two-dimensional model of the plasmasphere: refilling time constants, {\it Planet. Space Sci., 41}, 35, 1993. 
\\
5. Stern, D. P., The motion of a proton in the equatorial magnetosphere, {\it J. Geophys. Res., 80}, 595, 1975.
\\
6. Volland, H., A semiempirical model of large-scale magnetospheric electric fields, {\it J. Geophys. Res., 78}, 171, 1973.
\\
7. Weimer, D. R., An improved model of ionospheric electric potentials including substorm perturbations and application to the geospace environment modeling November 24, 1996, event, {\it J. Geophys. Res., 106(A1)}, 407, 2001.
\\
8. Welling, D. T., V. K. Jordanova, S. G. Zaharia, A. Glocer, and G. Toth. The effects of dynamic ionospheric outflow on the ring current. {\it Journal of Geophysical Research (Space Physics)}, 116, March 2011. doi:10.1029/2010JA015642.
\\
9. Welling, D. T., V. K. Jordanova, A. Glocer, G. Toth, M. W. Liemohn, and D. R. Weimer. The two-way relationship between ionospheric outflow and the ring current. {\it Journal of Geophysical Research:
Space Physics}, May 2015. ISSN 21699380. doi:10.1002/2015JA021231. 
\\
10. Young, D. T., H. Balsiger, and J. Geiss. Correlations of magnetospheric ion composition with geomagnetic and solar activity. {\it J. Geophys. Res., 87}, 9077, 1982.
\\
11. Zaharia, S., V. K. Jordanova, M. F. Thomsen, and G. D. Reeves. Self-consistent modeling of magnetic fields and plasmas in the inner magnetosphere: Application to a geomagnetic storm. {\it Journal of Geophysical Research (Space Physics)}, 111, A11S10, October 2006. doi:10.1029/2006JA011619.
\\
12. Engel, M. A., Morley, S. K., Henderson, M. G., Jordanova, V. K., Woodroffe, J. R., and Mahfuz, R. (2019). Improved simulations of the inner magnetosphere during high geomagnetic activity with the RAM-SCB model. Journal of Geophysical Research: Space Physics, 124, 4233–4248. doi:10.1029/2018JA026260\\

